% =====================================================================
%  Implementation section -- replaces the \todonote Implementation block.
%  All claims here are backed by the artifact (see README.md). No invented
%  numbers appear in this section.
% =====================================================================
\section{Implementation}
\label{sec:impl}

The artifact has two layers, separated so that the security claims do not depend
on any timing or hardware. (i)~A stdlib-only Python \emph{reference simulator}
implements the protocol logic---salted leaves, Merkle commitment, simulated
source endorsement, the on-chain anchor predicate, and the off-chain
verifier---and the adversarial coordinator. (ii)~A Hyperledger Fabric~2.5
\emph{deployment} implements the same protocol as Node chaincode:
\texttt{CommitWindow} on each source channel and \texttt{Anchor}\,/\,%
\texttt{GetAnchors} on the coordination channel.

\paragraph{Canonical encoding and determinism.}
Everything that is hashed uses an explicit, length-prefixed byte encoding rather
than JSON, because JSON number, whitespace, and key-order handling differs
across languages. A leaf is
$\leaff(e)=\Hh(\prf_{k_s}(\mathsf{eid}(e))\,\|\,\sigma(e))$ with
$\Hh=\text{SHA-256}$, $\prf=\text{HMAC-SHA256}$, and $\sigma$ a length-prefixed
concatenation of $(\mathsf{eid},\text{height},\text{txIndex},\text{domain},
\Hh(\text{payload}))$; the raw payload enters only via its hash, preserving
content confidentiality. The Python reference and the Node chaincode share this
encoding, and a cross-language conformance test verifies that the Node library
reproduces Python-generated vectors byte-for-byte (identical Merkle roots,
leaves, and commitment pre-images); it runs with \texttt{make conformance}.

\paragraph{Source channel: \texttt{CommitWindow}.}
Cross-domain-relevant events are recorded into an on-channel index; for window
$w$ over height range $[a,b]$, \texttt{CommitWindow} range-scans the index,
canonically orders the events by $(\text{height},\text{txIndex})$, computes
$\mroot^w_s$ and the count, and writes the commitment
$(s,w,[a,b],\mroot^w_s,\text{count})$. The transaction is endorsed under the
source channel's policy $P_s$, so the committed root is attested by an honest
quorum, not by the coordinator. The per-channel salt key $k_s$ is supplied via
Fabric transient data and is never written to the ledger.

\paragraph{Coordination channel: \texttt{Anchor}.}
\texttt{Anchor} verifies the source endorsement against a registered policy,
then enforces strict window monotonicity ($w=w^-{+}1$) and height contiguity
($a=b^-{+}1$) per source channel, rejecting at commit time otherwise.
\texttt{GetAnchors} is the verifier's read path. The endorsement check uses the
same keyed construction as the reference simulator for reproducibility; wiring
it to source-MSP ECDSA certificates (distributed via the on-chain registry) is
the single change required for a multi-MSP deployment and does not affect the
monotonicity/contiguity logic.

\paragraph{Reproducibility.}
Every experiment runs from a clean checkout. \texttt{make security} runs the
deterministic omission-detection battery; \texttt{make conformance} runs the
cross-language vector check; \texttt{make test} runs the unit tests;
\texttt{make tables} regenerates the LaTeX tables in this paper from the result
JSON. The Fabric latency measurements require the single-host network in
\texttt{network/README.md} and are produced by \texttt{bench/bench\_fabric.js}.
